Results

### 2022-05-15 article/results.Rmd
revise intro,bibs

Median plot wood density tended to increase marginally significantly 
(`r glue("p=",round(as.numeric(wd$pval),3))`) 
with edge distance by 
`r round(wd$statPrint[[1]]$estimate[[2]],4)` ± 
`r round(wd$statPrint[[1]]$std.error[[2]],5)` per m 
*(Fig \@ref(fig:biomass)b)*.

>>>>

Median plot wood density tended to increase marginally significantly 
(`r glue("p=",round(as.numeric(wd$pval),3))`) 
with edge distance by 
`r round(wd$statPrint[[1]]$estimate[[2]],4)` ± 
`r round(wd$statPrint[[1]]$std.error[[2]],5)` per m 
explaining 
`r "R2x100"`% of variance 
among median distance strata values
*(Fig \@ref(fig:biomass)b)*.
